---
title: "R Project 1 - Hello R"
author: "Dr. Katherine Shoemaker"
date: "1/23/2020"
output: 
  html_document: 
    fig_height: 3
    fig_width: 5
    highlight: espresso
    theme: cosmo
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1. 

(there are 142 rows and 2 columns. 26 variables)

### Exercise 2



#plot x vs y data dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3


#plot x vs y star dataset:

```{r plot-star, fig.height=3, fig.width=6}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#calculate the correlation between `x` and `y` in this dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))


```

I'm some text, you should replace me with more meaningful text...



### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

#plot x vs y circle dataset:

```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#calculate the correlation between `x` and `y` in this dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))


```

```{r}
```

```{r}
```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)

```{r}

ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
  theme(legend.position = "none")
```

```{r}
  
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```


