---
title: "R Project 1 - Hello R"
author: "Dr. Katherine Shoemaker"
date: "1/23/2020"
output: html_document
---

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1. 

(there are 1846 rows and 2 columns. The variables are mean, standard deviation, and correlation)

### Exercise 2



#plot x vs y data dino dataset:

```{r plot-dino, fig.height=3, fig.width=6}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3


#plot x vs y tiger dataset:

```{r plot-away, fig.height=3, fig.width=6}
away_data <- datasaurus_dozen %>%
  filter(dataset == "away")
ggplot(data = away_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#calculate the correlation between `x` and `y` in this dataset:

```{r cor-away}
away_data %>%
  summarize(r = cor(x, y))


```

I'm some text, you should replace me with more meaningful text...



### Exercise 4

(Add code and narrative as needed. Note that two R chunks are given but they are not labeled. Use the convention from above to name them appropriately.)

#plot x vs y circle dataset:

```{r plot-circle, fig.height=3, fig.width=6}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#calculate the correlation between `x` and `y` in this dataset:

```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))


```

```{r}
```

```{r}
```

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, green C+.)

? datasaurus_dozen
